The Cost of Transportation : Spatial Analysis of US Fuel Prices

### 2017-03-26 Docs/Paper/paper.tex
results_moran

@@

\comment{zip level data : check if stations without zip}

\comment{prices for different carburants and purchase mode $\rightarrow$ maybe take the most frequent for now ? on an example dataset (ts 1484114402), we have 89\% of credit (against cash on all records). For fuel type, it is more evenly distributed : 34\% for Regular, 22\% for Premium, 23\% for midgrade, 19\% for diesel. Maybe for the sake of simplicity work with Regular type and credit only. on the same example dataset, 96\% of stations have conjointly both, what gives a good coverage with this choice.}

>>>>

Papier de Gautier et Saoult \cite{gautier2015dynamics}

@@

The dataset comprises around $41\cdot 10^6$ unique observations, spanning in time from 2017-01-10 to 2017-03-19, that correspond to 118573 unique retail stations for each the geographical location (city resolution) was obtained. \comment{statistics of observation per station ?} Prices correspond to an unique purchase mode (credit card, other modes such as cash being less than 10\% in test datasets, they were discarded in the final dataset) and four fuel types: Diesel (18\% of observations), Regular (34\%), Midgrade (24\%) and Premium (24\%). The best coverage of stations is for Regular fuel type (\comment{recompute proportion on full dataset}), and we choose to work with this one in our exploratory analysis, keeping in mind that further developments with the dataset may include comparative analysis on fuel types.
